---
title: "Homework 5"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Prop test for a single city: 

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



## Problem 2 

import one dataset 

```{r}
data_1 = read_csv("data/con_01.csv")
```

```{r}
path_df = 
  tibble(
    path = list.files("data")
  ) %>% 
  mutate(
    path = str_c("data/", path),
    data = map(.x = path, ~read_csv(.x))) %>% 
  unnest(data)
```

Next I will tidy the unnested data: 

```{r}
path_tidy = 
  path_df %>% 
  separate(path, into = c("folder", "arm"), sep = 5) %>% 
  separate(arm, into = c("arm", "id"), sep = "_") %>% 
  separate(id, into = c("id", "file"), sep = 2) %>% 
  select(-folder, -file) %>% 
  mutate(
    id = str_remove(id, "0")
  ) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week", 
    values_to = "value",
    names_prefix = "week_"
  )
```

Next I will create the spaghetti plot: 

```{r}
data_plot = 
  path_tidy %>% 
  mutate( 
    arm = str_replace_all(arm, c("con" = "contol", "exp" = "experimental"))
   ) %>% 
  group_by(arm, id) %>% 
  ggplot(
    aes(x = week, y = value, group = id, color = id)) + 
  geom_point() +
  geom_line() + 
  geom_point(alpha = 0.5) + 
  facet_grid(arm ~.)
```


## Problem 3

```{r, error=TRUE}
n = 30
sigma = 5
mu = 0
t_test = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>%
    t.test() %>% 
    broom::tidy()
}

sim_results = 
  rerun(5000, t_test(mu = 0)) %>% 
  bind_rows()
sim_results %>% 
  select(estimate, p.value)

repeat_simulation = 
  tibble(mean = c(0,1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x = mean, ~rerun(5000, t_test(mu = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)
repeat_simulation %>% 
  select(mean, estimate, p.value)



